A Constraint Solving Approach to Parikh Images of Regular Languages

### 2023-06-06 introduction.tex
Use a nice green colour rather than slashes to denote regexes
Closes: #41

We use standard PCRE regular expressions here and throughout the paper, writing
them $\Regex{\texttt{in brackets}}$ to make that apparent. As is common,
$\RegexOr{}$ is alternation, $\mathtt{*}$ the Kleene star, and $\mathtt{.}$,
matches any single character.

>>>>

We use standard PCRE regular expressions here and throughout the paper, writing
them $\Regex{\texttt{like this}}$. This means that $\RegexOr{}$ is alternation,
$\mathtt{*}$ the Kleene star, and $\mathtt{.}$, matches any single character.
